% LaTeX resume using res.cls
\documentclass[line,margin]{res} 

\usepackage{color}
\definecolor{db}{rgb}{0,0,.4}
\definecolor{lb}{rgb}{0,0,.7}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}


\name{\color{lb}{Yadu Nand B}}
% \address used twice to have two lines of address

\address{\color{db}{yadudoc1729@gmail.com}\\}
\address{ +91 94477 80725}

%\address{Yadukul ,Plot \#1 ,Diwanpuram Hsg Colony}
%\address{Moolavattom P.O. Kottayam PIN: 686026}

 
\begin{resume}
 
\section{CAREER OBJECTIVE}
    To be part of a reputed organisation where cutting edge 
    technology and development in Computer Science is undertaken.
    I endeavour to apply my skills as an engineer to make 
    meaningful contributions to the community.       
 
\section{EDUCATION} {\sl Bachelor of Technology}\hfill Present,2007-2011\\
% \sl will be bold italic in New Century Schoolbook (or
% any postscript font) and just slanted in
% Computer Modern (default) font
   College of Engineering, Trivandrum \\
   Computer Science and Technology\\
   Expected completion: Summer 2011\\
   {\bf CGPA  : 7.4/10 }\\
   S4 GPA : 7.1 \\
   S3 GPA : 7.8 \\
   S1-S2 GPA: 7.3\\ 
   \\
   {\sl Junior College} \hfill 2005-2007\\
   St.Antony's Public School, Anakkal\\
   Physics, Chemistry, Maths, Computer Science option\\
   AISSCE Aggregate : 93.6\% \\
   \\
   {\sl High School} \hfill 2005\\
   Girideepam Bethany Central School, Kottayam\\
   AISSE Aggregate : 94.6\% 

\section{COMPUTER \\ SKILLS} {\sl Languages:} C ,C++ ,BaSH ,\LaTeXe ,NVIDIA-CUDA \\
   {\sl Database:} PL/SQL ,SQL\\
   {\sl Tools:} Git, gdb \\
   {\sl Operating Systems:} Dif\mbox{}ferent linux flavours,Windows 7,Vista
 
\section{EXPERIENCE} {\sl Natural User Interface Project} \hfill Winter, 2010 \\
    Funded by CS dept,CET\\
    Best Project Award, CETEX 2010.
    \begin{itemize}  \itemsep -2pt % reduce space between items
    \item 
      Implemented a cheap alternative to conventional multitouch 
      screens using IR Pens. The project involved designing and 
      improvising hardware as well as modifying OpenSource,Natural 
      User Interface sof\mbox{}tware to work with the hardware. 
   \end{itemize}
 
   {\sl Project Blinkenlights} \hfill            Winter, 2010 \\
   Funded by CS dept, CET
   \begin{itemize}  \itemsep -2pt %reduce space between items
   \item 
     Project blinkenlights uses an 16x8 LED panel which is fully 
     programmable. The panel can be controlled from a GUI to display 
     text, images, animation etc.The project involved hardware wiring 
     and interfacing with a computer as well as GUI development using
     Qt libraries.
   \end{itemize} 
                 
   {\sl Mini-Project : Distributed Video Encoding} \hfill        Fall, 2009 \\
   \begin{itemize}
   \item Conducted research,design and implementation of a Distributed 
     Video Encoding sof\mbox{}tware as Mini-Project. The sof\mbox{}tware reduces the 
     encoding time of large video f\mbox{}iles by distributing the
     processing load over several computers in a local area network. The 
     sof\mbox{}tware developed in C using operating system, multimedia and
     networking concepts extensively.
   \end{itemize} 
 
\section{HONORS \\AND\\ AWARDS}          
    Award for best project at CETEX 2010   \\      
    National Talent Search Scholar \\
    Open Source University Meetup ,Leader at CET 
	
\section{EXTRA-CURRICULAR \\ ACTIVITIES}             
    Founded {\bf FOSSCET}, The FOSS club of CET \\
    Organised several sessions as part of {\bf FOSSCET} club activities\\
    Conducted {\sl HashBang }, A bash scripting event at Aavishkar 2009\\
    Active member of FSUG-TVM \\
    
\section{PARTICIPATION}
    Indian Science Congress , Delegate  \hfill Trivandrum \\
    International Workshop on Distributed Systems , Delegate \hfill IIT Madras \\
    FOSS.in , Delegate , \hfill Bangalore     \\
    Hackfest at Shaastra 2009 \hfill IIT Madras \\
    FOSSTER 2009 , Delegate \hfill Amrita Vishwa Vidyapeetham ,Kollam \\
			
			
\section{PERSONAL DETAILS} 


\end{resume}
\end{document}







