\documentclass[line,margin]{res}

\usepackage{color}

\begin{document}
\name{Joji Antony}


\address{joji\_antony@gmx.com}
\address{+91 96323 41954}

\begin{resume}

\section{Profile}
Software Engineer with 4+ years experience working with technologies on the JVM platform, various JavaScript frameworks, C/C++ libraries and Perl based automation. Proficient in developing systems and application software that have requirements of high stability and large scale.

\section{Education}
{\bf Undergraduate College Education}\\
College of Engineering, Trivandrum\\
Bachelor of Technology in Computer Science and Engineering\\

\section{Technologies}

{\bf Programming Languages}\\
Java, Scala, C++, C, Perl, JavaScript, Assembly, Latex, Python

{\bf Frameworks}\\
Java EE, Hibernate, Perl Dancer, Flask, Various Javascript frameworks and libraries.

{\bf Tools}\\
MySQL, Postgres, UNIX tool chain, Jboss, Git, Subversion, Maven, vim, Intellij, Solaris MDB, Wireshark etc


\section{Work Experience and Projects}

Employed by Hewlett-Packard R\&D since August 2011\\

{\bf HP NMC Developer/Lead} \hfill {\it{2013 - Current}}\\
Currently working as a core developer for HP's Network Management Software called Network Node Manager i\\
Also currently working as lead developer and lab support engineer for NNMi NET SPI\\

{\it{Accomplishments}}\\
\begin{itemize}
\item Improving SNMP v3 USM specification compliance in our SNMP stack
\item Work on enabling NNMi to handle Network Function Virtualization.
\item Port the NET plugin to Linux; including build and test infrastructure.
\item Add support for NNMi for Safari on Mac.
\item Refreshing the NNMi UI as per the new UX guidelines.
\end{itemize}

{\it{Technologies}}\\
Java EE, SOAP, REST, JavaScript Dojo framework, Java Swing, etc\\

{\bf HP Network Node Manager 7.x lab support} \hfill {\it{2011 - 2013}}\\
Lab support engineer for Hewlett-Packard's premier Network Management Solution called NNM.\\

{\it{Accomplishments}}\\
\begin{itemize}
\item Added support for filtering based on parameters like 'hostname' in the Applet based UI.
\item Solved many multi-threading issues that were frustrating customers for years.
\item Solved many cache coherence issues.
\end{itemize}

{\it{Technologies}}\\
C, C++, Perl, Java, SQL, SPARC, PA-RISC, HP-UX, Linux, Solaris.

\section{Side projects}
{\bf Serenity} \hfill \it{2015-Present}\\
Simple Wiki software in Perl Dancer\\
https://github.com/simula67/serenity\\

{\bf SIC assembler} \hfill \it{2010}\\ 
Assembler for hypothetical SIC machine.\\
https://github.com/simula67/sasm\\


\section{Open source work}
{\bf Perl 6 LWP}\\
Merged a patch to Perl 6 LWP to match output of Perl 5 LWP\\
https://github.com/simula67/perl6-lwp-simple\\ \\
{\bf Perl 6 Test Suite}\\
Merged a patch to refactor some of Perl 6 official test suite\\
https://github.com/simula67/roast\\ \\
{\bf Snaplr packaging for Chocolatey}\\
Packaging Snaplr for chocolatey\\
https://github.com/simula67/chocolateytemplates\\


\section{Online Profiles}
{\bf Github :} \it{www.github.com/simula67} \\ \\ 
{\bf LinkedIn :} \it{https://in.linkedin.com/in/antonyjoji} \\ \\
{\bf Blog :} \it{https://simula67.wordpress.com/} \\

\end{resume}
\end{document}
